Throughput Prediction on 60 GHz Devices for Latency Sensitive Applications

### 2021-01-21 paper.tex
changes

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage{multirow}
\begin{table*}[t]
\caption{Requirements of Latency Sensitive Applications}
\label{tab:apps}
\begin{tabular}{@{}cc|c|c|c@{}}
\toprule
                                      &    & Bandwidth      & Latency                         & QoE                                                                                                                      \\ \midrule
\multirow{2}{*}{Virtual Reality}                   & 4K & 300 Mbps       & \multirow{2}{*}{16 ms (60 fps)} & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Motion-to-photon latency \textless 20 ms, frame rate 60 fps\end{tabular}}    \\
                                      & 8K & 1.2 Gbps       &                                 &                                                                                                                          \\ \midrule
\multirow{2}{*}{360\degree~video streaming} & 4K & 50 Mbps        & \multirow{2}{*}{33 ms (30 fps)} & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Motion-to-photon latency \textless 20 ms, frame rate 30-60 fps\end{tabular}} \\
                                      & 8K & 200 Mbps       &                                 &                                                                                                                          \\ \midrule
Live streaming                        & 4K & Up to 1.8 Gbps & 33 ms (30 fps)                  & Frame rate 30-60 fps                                                                                                     \\ \bottomrule
\end{tabular}
\end{table*}
% Motivation
% Need throughput prediction to do adaptation
% to maintain QoE
% Table with BW, Latency, QoE requirements
Applications such as VR, 360\degree~video streaming, live video streaming need to maintain a certain latency in order to provide the user with an acceptable quality of experience (QoE). Table~\ref{tab:apps} lists the requirements for these applications in terms of bandwidth, latency and QoE.

@@

@@

Table~\ref{tab:apps} details the requirements of latency sensitive applications in terms of the bandwidth, latency and QoE. As we can see, there are applications like 8K VR and live video streaming which require Gbps throughputs. Since current generation WiFi is not capable of delivering those speeds, 60 GHz wireless is a prime candidate to fulfil these needs. But, due to the nature of 60 GHz wireless, throughput prediction becomes rather important as ABR schemes would find it difficult to react to the sudden throughput changes inherent at such a high frequency. Note that these throughput changes also make the prediction of throughput at 60 GHz quite challenging.\Comment{this paragraph doesn't seem to belong here}

>>>>

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage{multirow}
\begin{table*}[t]
\caption{Requirements of Latency Sensitive Applications}
\label{tab:apps}
\begin{tabular}{@{}cc|c|c|c@{}}
\toprule
                                      &    & Bandwidth      & Latency                         & QoE                                                                                                                      \\ \midrule
\multirow{2}{*}{Virtual Reality}                   & 4K & 300 Mbps       & \multirow{2}{*}{16 ms (60 fps)} & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Motion-to-photon latency \textless 20 ms, frame rate 60 fps\end{tabular}}    \\
                                      & 8K & 1.2 Gbps       &                                 &                                                                                                                          \\ \midrule
\multirow{2}{*}{360\degree~video streaming} & 4K & 50 Mbps        & \multirow{2}{*}{33 ms (30 fps)} & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Motion-to-photon latency \textless 20 ms, frame rate 30-60 fps\end{tabular}} \\
                                      & 8K & 200 Mbps       &                                 &                                                                                                                          \\ \midrule
Live streaming                        & 4K & Up to 1.8 Gbps & 33 ms (30 fps)                  & Frame rate 30-60 fps                                                                                                     \\ \bottomrule
\end{tabular}
\end{table*}
% Motivation
% Need throughput prediction to do adaptation
% to maintain QoE
% Table with BW, Latency, QoE requirements

Applications such as VR, 360\degree~video streaming, and live video
streaming need to maintain a certain latency in order to provide the
user with an acceptable quality of experience
(QoE). Table~\ref{tab:apps} lists the requirements for these
applications in terms of bandwidth, latency and QoE.

@@

Table~\ref{tab:apps} details the requirements of latency sensitive
applications in terms of the bandwidth, latency and QoE. As we can
see, there are applications like 8K VR and live video streaming which
require Gbps throughputs. Since the current generation of WiFi is not
capable of delivering those speeds, 60 GHz wireless is a prime
candidate to fulfil these needs. But, due to the nature of 60 GHz
wireless, throughput prediction becomes rather important as ABR
schemes would find it difficult to react to the sudden throughput
changes inherent at such a high frequency. Note that these throughput
changes also make the prediction of throughput at 60 GHz quite
challenging.\Comment{this paragraph doesn't seem to belong here?}

@@
